Open Source, Collaborative Curriculum

### 2017-04-29 siip.tex
table budget

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage[hidelinks]{hyperref}

@@

          \section{Timeline and Deliverables}

@@

@@

\begin{tabular}[htb]{|l|c|c|c|}
        \hline
        \textbf{Item} & \textbf{Cost} & \textbf{Units} & \textbf{Notes} \\ 
        \hline
        \textbf{Lodging} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \textbf{<++>} & <++> & <++> & <++> \\ 
        \hline
\end{tabular}

>>>>

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}

@@

          \section{Timeline and Deliverables}
          \subsection{Timeline}
          The timeline will be bookended by two workshops, a kickoff workshop 
          and a retrospective workshop. In the intervening time, consistent 
          communication through GitHub's collaboration framework, a Slack 
          channel, an email listhost, a shared Google Drive folder, and

@@

          \subsection{Deliverables}

          \subsubsection{Learning Objectives List}
          \subsubsection{Concept Map}
          \subsubsection{Learning Dependency Graph}
\begin{figure}[htb!]
        \begin{center}
                \includegraphics[height=0.5\textheight]{rosalind.png}
        \end{center}
        \caption{Rosalind.info has a graph of exercises and their dependencies.}
        \label{fig:rosalind}
\end{figure}
          \subsubsection{Lesson Materials}

@@

\begin{table}[htb]
        \begin{tabularx}{\textwidth}{| X |c|c|c|c|c|}
        \hline
        \textbf{Event} & \textbf{Item} & \textbf{Cost} & \textbf{Units} & \textbf{\$} & \textbf{Notes}\\ 
        \hline
Kick-off Workshop&Meeting Room&744&2&1488&Allerton, all day package\\
&Lodging&150&24&3600&Allerton guest rooms\\
&Flights&800&6&4800&Estimated\\
&Taxi&20&12&240&\\
&Incidentals&100&6&600&\\
&Continental breakfast&8.5&24&204&Working breakfasts, Allerton\\
&Dinner&30&24&720&In Champaign-Urbana\\
\hline
Retrospective Workshop&Meeting Room&50&2&100&Illini Union\\
&Projector&300&4&1200&Illini Union\\
&Lodging&150&24&3600&Illini Union Hotel\\
&Flights&800&6&4800&Estimated\\
&Taxi&20&12&240&\\
&Incidentals&100&6&600&\\
&Continental breakfast&8.5&24&204&University Catering\\
&Coffee Service&32.5&4&130&\\
&Lunch&15&24&360&University Catering\\
&Dinner&30&24&720&In Champaign-Urbana\\
        \hline
        &\textbf{Total}&&&\textbf{23606}&\\
        \hline
\end{tabularx}
\end{table}
